---
title: "DS202_Lab1Haoxuan Cai"
author: "Haoxuan Cai"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Understanding Concepts 

1.Git competes with centralized and distributed version control tools such as Subversion, Mercurial, ClearCase and IBM's Rational Team Concert. On the other hand, GitHub competes with cloud-based SaaS and PaaS offerings, such as GitLab and Atlassian's Bitbucket.

2. Yes. They are independent software and design for each other.

3.  A git repository contains, among other things, the following: A set of commit objects. A set of references to commit objects, called heads.

In the upper-right corner of any page, click , and then click New repository.

Type a short, memorable name for your repository. ...

Optionally, add a description of your repository. ...

Choose to make the repository either public or private. ...

Select Initialize this repository with a README.

Click Create repository.

# Coding Exercises 

1.
```{r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(X)==TRUE)

```

2.

```{r}

   age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   example_data
   example_data[3,3]<-150
   example_data
   
```

3.
```{r}
x<-c(NA,1:3,NA,8)
average<-function(x){
  a<-x/sum(x,na.rm=TRUE)
  print(paste"The mean of x is",a)
}

avgmean<-function(x){
  b<-mean(is.na(x))
  print(paste("The mean of True and FALSE is", b))
}

average(x)
avgmean(x)
```

4.
```{r}
both.na<-function(x,y){
  stopifnot(length(x)==length(y))
  which(is.na(x)&is.na(y))
}

y<-c(NA,1:3,NA,8)
both.na(x,y)
```

